---
title: "rkicolors - Unofficial Themes and Color Palettes for Plots based on the RKI Corporate Designs for R and ggplot2"
author: "Dr. Lars E. Kroll"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
fig_caption: no
fig_width: 6 
fig_height: 4 
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The package Vignette for the package `rkicolors` is a simple documentation on how to use the package to create `ggplot2` plots in line with the corportaty design of the Robert Koch Institut. Note however, that this theme is an unofficial application of the RKI Style  and must not be used to fake RKI results. 

## Vignette Info

Part of the package are two ggplot themes (`theme_rki()` and `theme_rki_void()`) as well as two ggplot scales (`scale_fill_rki()` and `scale_color_rki()`). The theme includes various color palettes based on the RKI corporate color ported to RGB. 


## Basic Libraries used for this Vignette

```{r, warning=FALSE}
library(devtools)
library(httr)
library(ggplot2)
library(dplyr)
library(extrafont)
library(maps)
library(mapdata)
```


## Installation

Note: This guide assumes that you are behind a corporate firewall with a proxy server. If you are not, you might skip the `httr` Proxy Configuration.

```{r, eval=FALSE}
myproxy <- Sys.getenv("http_proxy")
httr::set_config(httr::use_proxy(myproxy))
devtools::install_github("lekroll/rkicolors")
```

## Basic Usage
```{r, warning=FALSE}
library(rkicolors)
```

```{r,  fig.height = 4, fig.width = 6, fig.align ="left"}
sampleplot <- ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +   geom_point() 
sampleplot
```


```{r,   fig.height = 4, fig.width = 6, fig.align ="left"}
sampleplot +  theme_rki() + scale_color_rki()
```
Change the colors to a different, RKI based Palette:
```{r,  fig.height = 4, fig.width = 6, fig.align ="left"}
sampleplot +  theme_rki() + scale_color_rki("qualitative")
```

## Using the right fonts
Apply the RKI Corporate "ScalaSans" Fonts to the Plot if they are available on the local machine. Note `font_import()` may take a while, depending on the number of fonts installed on the local machine. As a limitation, only True Type Fonts are acceptable by `extrafont`. 

Check if Scala is available:
```{r, warning=FALSE}
# uncomment only on first run
# font_import(prompt = FALSE) 
# loadfonts() 
fonttable() %>% as.data.frame() %>% filter(grepl("Scala", FullName)) %>% select(FamilyName,FullName,Bold,Italic,Symbol)
```

Apply font to theme:

```{r,   fig.height = 4, fig.width = 6, fig.align ="left"}
sampleplot +  
  theme_rki(base_family="ScalaSansLF-Regular", bold_family="ScalaSansLF-Bold", base_size = 10) + 
  scale_color_rki("qualitative")
```

## Color Options
The color schemes below can be applied using `scale_fill_rki(COLOR_SCHEME_NAME)`. If the fill or color variable is not discrete, `scale_fill_rki(COLOR_SCHEME_NAME, discrete=FALSE)` has to be used.


```{r,  fig.height = 1, fig.width = 6, fig.align ="left", echo=FALSE}
explot <- as.data.frame(cbind("x"=seq(1:128),"y"=1)) %>%
  ggplot(.,aes(x=x,y=y,fill=x)) + geom_bar(stat="identity",width=1) + 
  theme_rki_void(bold_family="ScalaSansLF-Bold") + guides(fill=FALSE)
for (rkicolorsheme in names(rkicolors::rki_palettes)) {
  myplot <- explot + geom_text(aes(x=20,y=.5, label=paste(rkicolorsheme)),size=4,hjust="left",color="white") + 
          scale_fill_rki(paste(rkicolorsheme), discrete = FALSE)
  print(myplot)
}
```

## Working with continous outcomes
To apply the scales to continous outcomes, the parameter `discrete=FALSE` has to bet used:
```{r,  fig.height = 4, fig.width = 6, fig.align ="left"}
ggplot(iris, aes(y=Sepal.Width, x=Sepal.Length,color=Sepal.Width)) +   geom_jitter(size=3) +  guides(color=FALSE)+theme_rki(base_family = "ScalaSansLF-Regular",bold_family = "ScalaSansLF-Bold") + scale_color_rki("bluered",discrete=FALSE) + facet_grid(cols = vars(Species))
```



## Plot Maps
```{r ,fig.height = 4, fig.width = 6, fig.align ="left", warning=FALSE}
worldmap.df <- map_data("world") %>% filter(region!="Antarctica")
map <- ggplot(data = worldmap.df) + 
  geom_polygon(aes(x = long, y = lat, group = group, fill="All"), color = "white") + 
  coord_fixed() +   guides(fill=FALSE)  + 
  theme_rki(base_family="ScalaSansLF-Regular", bold_family="ScalaSansLF-Bold", base_size = 10) + 
  scale_fill_rki()
map
map + theme_rki_void()
```


## Apply theme to every new plot in a Session:
```{r,   fig.height = 4, fig.width = 6, fig.align ="left"}
theme_set(theme_rki(base_family="ScalaSansLF-Regular", bold_family="ScalaSansLF-Bold", base_size = 10))
sampleplot + scale_color_rki()
```
